### 2023-10-29 conclusions/conclusion.tex
Correcting inappropriate raccourcis and correcting design
added stuff to conclusion

More complex input sequences produce even more inaccuracies. Indeed, when working with sequence 15 (\cref{graph:io15Celegans}), the inaccuracies spiral up and gives out a barely usable prediction. The curve generated doesn't fit its digital counterpart anymore.

@@

@@

The values of \acp{LLM}, such as \ac{LLaMA}-2 \textbf{Meta}'s \ac{LLM} and the two last versions of \acp{GPT} the \ac{LLM} that powers \textit{ChatGPT}, were included to show how the area of the chip scales up. Those models don't use \acp{RNN}, and futhermore, give out ridiculous areas. Fabricating such cicuits in analog is not feasible witht the current technologies.

>>>>

More complex input sequences produce even more inaccuracies. Indeed, when working with sequence 15 (\cref{graph:io15Celegans}), the inaccuracies spiral up and gives out a barely usable prediction. The curve generated does not fit its digital counterpart anymore.

@@

\subsection{Execution time}

The inference time is quite tricky to deal with. While the analog circuit's inference time is set, it gets more complicated when trying to get the digital inference time. The digital inference time depends on the computer it is being run on. The \acp{CPU} used in embedded sytems, the main application for this work, are usually not very fast as they are intended to be low powered. This parts will thus only dicuss of the inference of the analog circuit.

\subsubsection{Airline inference}

The airline problem feeding two inputs to the circuit to get a single output, it will have to be run $144$ times to get all the output data.
The inference time depends on the serial size being used :

\begin{itemize}
  \item $n_s=1$ : The output can be read as a voltage on the output net from $t_0=18\mu s$ to $t_1=22\mu s$.
  \item $n_s=2$ : The output can be read as a voltage on the output net from $t_0=34\mu s$ to $t_1=38\mu s$.
  \item $n_s=4$ : The output can be read as a voltage on the output net from $t_0=66\mu s$ to $t_1=70\mu s$.
\end{itemize}

Those are the times it takes to compute one of the outputs. It takes $144$ times longer to get all of the results.

\subsubsection{\ac{C. elegans} inference}

This sequence is a bit more complicated, for every input sequence with a thousand time steps, there are a thousand output vectors being read. Here, the inference time also depends on the serial size.

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Serial size & $n_s=1$ & $n_s=2$ & $n_s=4$ & $n_s=8$\\
    \hline
    Start of first output & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    End of first output & $13\mu s$ & $21\mu s$ & $37\mu s$ & $69\mu s$\\
    \hline
    Output period & $9\mu s$ & $17\mu s$ & $33\mu s$ & $65\mu s$\\
    \hline
    Start of last output & $9ms$ & $17ms$ & $33ms$ & $65ms$\\
    \hline
    End of last output & $9ms +4\mu s$ & $17ms+4\mu s$ & $33ms+4\mu s$ & $65ms+4\mu s$\\
    \hline
  \end{tabular}
  \caption{First read values for the different serial sizes}
  \label{tab:readTimesCelegans}
\end{table}

\Cref{tab:readTimesCelegans} shows the output time ranges with thier period.

@@

The values of \acp{LLM}, such as \ac{LLaMA}-2 \textbf{Meta}'s \ac{LLM} and the two last versions of \acp{GPT} the \ac{LLM} that powers \textit{ChatGPT}, were included to show how the area of the chip scales up. Those models do not use \acp{RNN}, and futhermore, give out ridiculous areas. Fabricating such cicuits in analog is not feasible witht the current technologies.
